---
title: "Data 607 Assignment 3"
author: "Miguel Gomez"
date: "2023-02-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

<font size="5"> 
#1  Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"



-----------------------------------------------

<font size="5">Pulling Data


```{r}
data1<-read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv")
```

```{r}
data2 <- as.data.frame(data1)

```

<font size="5"> 

Adding the names of columns


```{r}
names(data2)= c("FOD1P", "Major", "Major_Category")

```


```{r}
head(data2)

```

<font size="5"> 

Selecting all Majors that contain either "DATA" or "STATISTICS"


```{r}
library(dplyr)
```


```{r}
dplyr::filter(data2,grepl('DATA|STATISTICS', Major))
```

<font size="2"> 

3 courses contain "DATA" or "STATISTICS".


<font size="5"> 
#2 Write code that transforms the data


```{r}
data3 <- c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

data3
```
```{r}
library(dplyr)
data4 <-as.data.frame(data3)

data4
```




<font size="5"> 
#3 What each expression will match

<font size="2">

(.)\1\1 - Character repeated 3 times in a row.

(.)(.)\\2\\1 - 2 characters followed by the same 2 characters in reverse order.

(..)\1 - 2 characters repeated twice

(.).\\1.\\1 - A character repeated 3 times with characters in between each repetition. 

(.)(.)(.).*\\3\\2\\1 - 3 characters followed by 0 or more characters of any kind followed by the same 3 characters but in reverse order.

----------------------------------------------
<font size="5"> 
#4 Construct regular expressions to match words that...

<font size="2"> Start and end with the same character: ^(.).*\\1$


Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.): "(..).*\\1


Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.): "([a-z]).*\\1.*\\1