---
title: "Data 607 Assignment 1"
author: "Miguel Gomez"
date: "01-29-2023"
output: html_document
---

---<font size="4"> 
Due to the ongoing climate surrounding police interactions with civilians, I decided to review the article  "Where Police Have Killed Americans In 2015" by Ben Casselman. This articles focuses on the demographic and economic information of the neighborhoods where these police killings occurred. 

Link:https://fivethirtyeight.com/features/where-police-have-killed-americans-in-2015/

---

---<font size="5"> 

Pulling Data

---

```{r}
data1<-read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/police-killings/police_killings.csv")

```

```{r}
data2 <- as.data.frame(data1)
```

---<font size="5"> 

Adding the names of columns
---

```{r}
names(data2)= c("name", "age", "gender", "raceethnicity","month","day","year","streetaddress","city", "state", "latitude", "longitude", "state_fp","county_fp","tract_ce", "geo_id", "county_id", "namelsad", "lawenforcementagency",  "cause", "armed", "pop", "share_white", "share_bloack", "share_hispanic", "p_income", "h_income", "county_income", "comp_income", "county_bucket", "nat_bucket", "pov", "urate", "college")
```

```
head(data2)
```

---<font size="5"> 

Selecting ethnicity data
---

```{r}
raceethnicitycounts <- table(data2$raceethnicity) 
```

---<font size="5"> 

Counts how many times each ethnicity  shows up
---

```{r}
raceethnicitycounts
```

---<font size="5"> 

Labels for ethnicities
---

```{r}
raceethnicitycountslabels <- c("Asian/Pacific Islander", "Black", "Hispanic/Latino", "Native American",  "Unknown",  "White")
```

---<font size="5"> 

Calculates ethnicity counts percentages
---


```{r}
raceethnicitycountsratio <- raceethnicitycounts/sum(raceethnicitycounts)
```

---<font size="5"> 

Converts ethnicity counts to percentages
---

```{r}
pct <- round(raceethnicitycountsratio/sum(raceethnicitycountsratio)*100)
```

---<font size="5"> 

Adds percentages to labels
---
```{r}
raceethnicitycountslabels <- paste(raceethnicitycountslabels, pct)
```

---<font size="5"> 

Adds % to labels
---

```{r}
raceethnicitycountslabels  <- paste(raceethnicitycountslabels, "%", sep="")

```

---<font size="5"> 
I decided to include a pie chart that breaks down the people killed by ethnicity. Even though majority of the police killings occurred in neighborhoods that are poorer and blacker, 51% of the people killed were white. 
---
```{r}
pie(pct, labels = raceethnicitycountslabels, main = "2015 Police Killings by Ethnicity")
```

---<font size="5"> 

Counts how many times each weapon shows up

---

```{r}

weaponcounts<- table(data2$armed)

```

---<font size="5"> 

Calculates weapon counts percentages
---

```{r}
weaponratios <- weaponcounts/sum(weaponcounts)

```

---<font size="5"> 

Converts weapon counts to percentages
---

```{r}
pct2 <- round(weaponratios/sum(weaponratios)*100) 

```
 
```{r}

barplot(pct2, horiz=T, xlim = c(0,50) ,las=1,  main = "Weapons people killed by police were armed with", xlab= "Number of People Armed",  cex.names=.5)
 
```

---<font size="5"> 

In addition, I added a bar plot that shows what weapons the people killed by the police were armed with. Majority of them also had guns. 
---

